---
title: Discrete Math Model by ANU
author:
  - name: Nanthawat Anancharoenpakorn
abstract:
  - "**Motivation: ** Learn how to develop discrete math model to solve or represent abstract thing."
  - "**How to apply: ** When solving a problem, we need to simplify the world into a model. This course explain how to represent object, process and algorithm to solve the problem."

bibliography: mybibfile.bib # Includes refs in OUP example template
## When using `citation_package = "default"`, a CSL file can be used
#csl: https://www.zotero.org/styles/oxford-university-press-note
output:
  rticles::oup_article:
    oup_version: 1 # 1 = 2020 CTAN OUP CLS package; 0 = 2009 OUP CLS package
    journal: "Discrete Math Model"
    document_style: "contemporary" # Can be contemporary, modern, traditional
    papersize: "large" # Can be large, medium, small
    #citation_package: "default" # Uncomment when using a CSL; default "natbib"
    namedate: FALSE # Set FALSE to use numeric refs; Default FALSE
    #number_sections: FALSE # Uncomment to not number sections; default TRUE
    #number_lines: TRUE # Use `lineno` package - Default FALSE
    #number_lines_options: ["mathlines","switch"]  # Options for latex lineno package.
    #onecolumn: TRUE # Uncomment for one column format; default FALSE
    extra_dependencies:
      - booktabs # to use with knitr::kable() example below
      
## Example of pandoc's variable
#urlcolor: orange
#linkcolor: green
#citecolor: red
header-includes:
  #- \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
  - \theoremstyle{thmstyleone} # Theorem stuff from OUP template
  - \newtheorem{theorem}{Theorem} #  meant for continuous numbers. %%\newtheorem{theorem}{Theorem}[section] # meant for sectionwise numbers. optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
  - \newtheorem{proposition}[theorem]{Proposition} # %%\newtheorem{proposition}{Proposition}" # to get separate numbers for theorem and proposition etc.
  - \theoremstyle{thmstyletwo}
  - \newtheorem{example}{Example}
  - \newtheorem{remark}{Remark}
  - \theoremstyle{thmstylethree}
  - \newtheorem{definition}{Definition}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, # By default, hide code; set to TRUE to see code
  fig.pos = 'th', # Places figures at top or here
  out.width = '100%', dpi = 300, # Figure resolution and size
  fig.env="figure"
) # Latex figure environment

options(knitr.table.format = "latex") # For kable tables to write LaTeX table directly
```

# Representation

## Object

1.  set = $\{ 1, 2, 3\}$

2.  multiset $= \{1,2,3,3\}$

3.  sequence = (1,2,3,4)

4.  tuple = (1,2)

5.  matrix $A = \begin{bmatrix} a_1 & a_2 \\ b_1 & b_2 \end{bmatrix}$

## Relation

1.  **Relation** is a relation $R$ from object a to Object b or $a R b$
2.  **Function** is a special type of relation. A function $f(x) = x$

# Graph Theory

## Object

1.  vertex

## Object

2.  edge
3.  direct edge
4.  weight edge

# Code

```{r, echo = TRUE}
set = c(1,2,3)
multiset= c(1,2,3,3)
sequence = 1:10
sequence = seq(from = 1, to = 10, by = 1)
tuple = list(1, "word", TRUE)
matrix = matrix(c("a1","a2", "b1", "b2"),
                nrow = 2, ncol = 2, byrow = FALSE)
```

## Generate a table using `xtable`

```{r xtabletable, results="asis", echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# Creates tables that follow OUP guidelines 
# using xtable
library(xtable) 
print(xtable(df,caption="This is a xtable table.",
             label="tab:tab1"),
      comment=FALSE,caption.placement="top")
```

You can reference this table as follows: Table \ref{tab:tab1}.

## Generate a table using `kable`

```{r kabletable, echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# kable can alse be used for creating tables
knitr::kable(df,caption="This is a kable table.",
             booktabs=TRUE,label="tab2")
```

You can reference this table as follows: Table \ref{tab:tab2}.

## Table spanning two columns

Tables can span two columns be setting `table.envir = "table*"` in `knitr::kable`.

```{r widetable, echo=TRUE}
df = data.frame(ID=1:3,code1=letters[1:3],
                code2=letters[4:6],
                code3=letters[7:9],
                code4=letters[10:12],
                code5=letters[13:15])

# kable can alse be used for creating tables
knitr::kable(df,caption="This is a wide kable table.",
             #format="latex",
             table.envir="table*",
             booktabs=TRUE,label="tab3")
```

# 
